Using Metric Space Indexing for Complete and Efficient Record Linkage

### 2017-11-21 paper.tex

\begin{figure}
\begin{verbatim}
This will be a table of Comparisons, F1, precision recall and pairs stuff.
12 ROWS ISH
\end{verbatim}
\caption{Linkage Quality on the Cora data set\label{comparison-of-results}}
\end{figure}

@@

>>>>

\begin{figure}
\begin{table}
\centering
\begin{tabular}{lllllllll}
Linker      & Linker             & Total comparisons & Number of links & Average pairs quality & Average pairs completeness & Precision & Recall & F1 Measure \\
Brute Force & Brute Force        & 1677025           & 12474           & 0.02                  & 0.33                       & 0.84      & 0.57   & 0.68       \\
MTree       & MTree              & 902693            & 12474           & 0.89                  & 0.22                       & 0.84      & 0.57   & 0.68       \\
LSH         & LSH-2-2            & 175435            & 10443           & 0.31                  & 0.29                       & 0.94      & 0.53   & 0.68       \\
LSH         & LSH-5-2            & 175435            & 10443           & 0.31                  & 0.29                       & 0.94      & 0.53   & 0.68       \\
LSH         & LSH-10-2           & 175435            & 10443           & 0.31                  & 0.29                       & 0.94      & 0.53   & 0.68       \\
LSH         & LSH-2-5            & 175435            & 10443           & 0.31                  & 0.29                       & 0.94      & 0.53   & 0.68       \\
LSH         & LSH-5-5            & 175435            & 10443           & 0.31                  & 0.29                       & 0.94      & 0.53   & 0.68       \\
LSH         & LSH-10-5           & 175435            & 10443           & 0.31                  & 0.29                       & 0.94      & 0.53   & 0.68       \\
LSH         & LSH-2-10           & 175435            & 10443           & 0.31                  & 0.29                       & 0.94      & 0.53   & 0.68       \\
LSH         & LSH-5-10           & 175435            & 10443           & 0.31                  & 0.29                       & 0.94      & 0.53   & 0.68       \\
LSH         & LSH-10-10          & 175435            & 10443           & 0.31                  & 0.29                       & 0.94      & 0.53   & 0.68       \\
Blocking    & Blocking-year      & 115893            & 6504            & 0.22                  & 0.19                       & 0.99      & 0.35   & 0.51       \\
Blocking    & Blocking-authors   & 11039             & 3219            & 0.74                  & 0.1                        & 0.94      & 0.16   & 0.28       \\
Blocking    & Blocking-title     & 27407             & 8225            & 0.84                  & 0.23                       & 0.95      & 0.42   & 0.58       \\
Blocking    & Blocking-venue     & 36647             & 6383            & 0.7                   & 0.12                       & 0.85      & 0.29   & 0.44       \\
Blocking    & Blocking-location  & 1009957           & 9551            & 0.17                  & 0.24                       & 0.83      & 0.43   & 0.57       \\
Blocking    & Blocking-publisher & 833079            & 9634            & 0.12                  & 0.23                       & 0.85      & 0.44   & 0.58       \\
Blocking    & Blocking-combined  & 1214269           & 12324           & 0.05                  & 0.32                       & 0.84      & 0.56   & 0.67      
\end{tabular}
\end{table}
\caption{Linkage Quality on the Cora data set\label{comparison-of-results}}
\end{figure}

@@

In this paper we have demonstrated the efficacy of the application of MSI to achieve complete and efficient record linkage, without the need for complex parameter tuning. In conclusion, this assertion deserves some careful unpacking. It is always possible to achieve high quality linkage using a brute-force approach. However the n-squared complexity of this approach prevents its practical application for datasets of even moderate size. The use of MSI techniques such as M-tree delivers the same results as the brute-force approach at the cost of
